Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2017-03-30 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
?

This manuscript highlights the many uncertainties involved in what appear to be simple fire experiments.  Uncertainties related to fuel type, measurement methods, and analysis techniques were examined.  The objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 s maximum), well characterized fires.  Three different fuels were used: natural gas, gasoline, and polyurethane foam.  Each fuel had a similar top surface area.  The heat release rate data showed that the variability between replicates was greater for more complex fuels.  The variation in peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, 11\%.  However, the variation in the peak heat release rates of the gasoline and the polyurethane foam increased due to increased uncertainties in the burning behavior of the fuels.

>>>>

This manuscript highlights the many uncertainties involved in what appear to be simple fire experiments.  Uncertainties related to fuel type, measurement methods, and analysis techniques were examined.  The objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 seconds maximum), well characterized fires.  Three different fuels were used: natural gas, gasoline, and polyurethane foam.  Each fuel had a similar top surface area.  The heat release rate data showed that the variability between replicates was greater for more complex fuels.  The variation in peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, 11\%.  However, the variation in the peak heat release rates of the gasoline and the polyurethane foam increased due to increased uncertainties in the burning behavior of the fuels.
